\section{Boolean Functions}
A boolean function is perhaps the most simplest function in computer science.

\begin{definition}[Boolean Function]
A function $f:\{0,1\}^n \righarrow \{0,1\}$ is called a boolean function.
\end{definition}

There are different ways to measure the complexity of a boolean function. 
Here we present four: \textbf{decision tree complexity, sensitivity, certificate complexity and degree}.

\begin{definition}[Decision Tree complexity]
The \textit{decision tree complexity} $d(f)$ of a boolean function is the depth of the smallest tree that computes a boolean function.
\end{definition}

\begin{definition}[Sensitivity]
    The hypercube is a graph that connects inputs of a boolean function $f$ which differ by 1 bit. 
    The nodes (inputs) in the hypercube are colored with the output of the boolean function.
    The \textit{sensitivity complexity} $s(f)$ is defined as the maximum number of neighbours with different color in the hypercube.
\end{definition}

\begin{definition}[Certificate Complexity]
A certificate is a set of coordinates in the input that once we fixed those coordinates, the value of the function
is determined. The \textit{certificate complexity} $c(f)$ is the smallest number such that every input $x$ has a certificate
of size $c(f)$.  
\end{definition}

\begin{definition}[Degree Complexity]
Any function $f:\{0,1\}^n righarrow \mathbb{R}$ can be expressed as a multilinear polynomial. The degree complexity 
$deg(f)$ of a boolean function is the degree of this polynomial.
\end{definition}

We can stablish bound between these complexity mesasures:

\begin{proposition}
    The following bounds hold:
    \begin{itemize}
        \item $s(f) \leq c(f)$
        \item $c(f) \leq d(f)$
        \item $deg(f) \leq d(f)$
        \item $d(f) \leq c(f)^2$
    \end{itemize}
\end{proposition}

